IRTF Spectro-Photometry of Rotating Brown Dwarfs

### 2016-10-28 ms.tex
I added 2MASS J0835's specphot image side by side with 2MASS J0835 for comparison.

\usepackage{natbib}

\newcommand{\vdag}{(v)^\dagger}

@@

\section{Light Curves}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\textwidth]{specphot_j1821.pdf}
\caption{Top Panel: 2MASS 1821's median spectrum compared with the reference star. The reference star is a significantly higher temperature star. Bottom Panel: Dynamic spectrum of 2MASS J1821.}\label{fig:DHSRes}
\end{figure}

>>>>

\usepackage{natbib}
\usepackage[caption=false]{subfig}
\newcommand{\vdag}{(v)^\dagger}

@@

\section{Light Curves}

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{specphot_j0835.pdf}
	\label{fig:specphot0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{specphot_j1821.pdf}
	\label{fig:specphot1821}
	}
	\caption{Top Panels: The target stars' median raw spectrum compared with the reference star. The areas near 1.4 and 1.8 $\mu$m are contaminated by telluric water absorption. The reference stars are significantly higher temperatures. Bottom Panels: Dynamic spectrum of 2MASS J1821.}
	\label{fig:corner}
\end{figure*}
